### 2023-04-19 main.tex
Q0Formula

Q_{2L}^{0}&=N\left(I^{tot}+2e_{11}^{tot}\right)+e_{11}^{tot}(2e_{11}^{tot}+I^{tot})-\sum_{j=2}^{N}e_{jj}^{tot}
+\sum_{i=2}^{N}\left(	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\right)
it has the property that commute with the equilibrium Hamiltonian

>>>>

Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
it has the property that commute with the equilibrium Hamiltonian. In case of $N=2$ it differs with respect to the $Q_{2L}^{0}$ computed in formula (2.28) of \cite{frassek2020eigenstates} by the following matrix 
Q_{2L}^{0,Francesco}-Q_{2L}^{0,Rouven}=	\begin{pmatrix}
		2&0&0&0\\
		0&-2&0&0\\
		0&0&-2&0\\
		0&0&0&2
